Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-08 draftfinalreport_v4.Rnw
11:17 WRITING updates from Dave

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{figures/naive_allPop_yob.pdf}
\end{center}
\caption{New Zealand population by year of birth and estimated numbers of na\"{\i}ve people in each age class using national immunity data (\autoref{table:sero}) (top) and the number of cases by year of birth (bottom).}
\label{fig:naive_yob}
\end{figure}

@@

\subsection{Summary of modelling}
\begin{itemize}
\item Regular introductions of measles pose an ongoing threat to New Zealand's efforts to eliminate measles (also see \autoref{sub:risk_analyses}).
\item The reproduction number for measles in the partially immune New Zealand population is often close to and exceeding one, suggesting increased population level immunity is required to ensure prevention of measles persistence following importation.
 \item The proportion of the currently na\"{\i}ve population requiring additional and effective vaccination in New Zealand required to push $R_v$ below one ranges from 17\% to 34\% among DHBs, and is 54\% at the national level (approximately 402,010 vaccinations).
\end{itemize}

>>>>

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{figures/naive_allPop_yob.pdf}
\end{center}
\caption{New Zealand population by year of birth and estimated numbers of na\"{\i}ve people in each age class using national immunity data (\autoref{table:sero}) (top) and the number of measles cases by year of birth from 2007--2014 (see \autoref{fig:ageandvac}) (bottom).}
\label{fig:naive_yob}
\end{figure}

@@

\subsection{Summary of modelling}
\begin{itemize}
\item Regular introductions of measles pose an ongoing threat to New Zealand's efforts to eliminate measles (also see \autoref{sub:risk_analyses}).
\item The reproduction number for measles in the partially immune New Zealand population is often close to and exceeding one, suggesting increased population level immunity is required to ensure prevention of measles persistence following importation.
 \item The proportion of the currently na\"{\i}ve population requiring additional and effective vaccination in New Zealand required to push $R_v$ below one is 54\% at the national level (approximately 402,010 vaccinations), but varies from a few thousand to >40,000 at the DHB level.
\end{itemize}
